\bf Title

### 2023-10-30 article/paper_padic_spec.tex
last modifs

\begin{definition}[Smith Normal Form] \label{smith_nf}
  Let $M \in \allmat_{m,n}(K)$ be of rank $r$. There exist unique integers $a_1 \leq \cdots \leq a_r$, and
  unique matrices $P \in \GL_n(\OK)$ and $Q \in \GL_m(\OK)$, such that
  $$
  S := QMP^{-1} = p^{a_1} \oplus p^{a_2} \oplus \cdots \oplus p^{a_r} \oplus {\bf 0}_{m-r}
  $$
  where ${\bf 0}_{m-r}$ is a null square matrix of size $m-r$.
  The matrix $S$ is called the {\it Smith Normal Form (SNF)} of $M$.
\end{definition}

\begin{remark}
  \begin{enumerate}%[label=\roman*.]
  \item The coefficient of the Smith normal form are unique and called \textit{invariant factors}.
  \item The valuation of the first coefficient of the Smith normal form of a matrix $M \in \mathcal{M}_n \left( \QQ_p \right) $ is the minimum of the valuations of the matrix $M$'s terms.
  \item In particular, the the normal Smith form of matrix of $\mathcal{M}_n \left( \OK \right) $ have coefficients in $\ZZ_p$ .
  \item The $r = \text{rank} M$ first diagonals coefficients of $S$ are exactly its non-zero coefficient.
  \end{enumerate}
\end{remark}

@@

>>>>

\begin{definition}[Smith Normal Form] \label{smith_nf}
  Let $M \in \allmat_{m,n}(K)$ be of rank $r$. There exist unique integers $a_1 \leq \cdots \leq a_r$, and
  unique matrices $P \in \GL_n(\OK)$ and $Q \in \GL_m(\OK)$, such that
  $$
  S := QMP^{-1} = p^{a_1} \oplus p^{a_2} \oplus \cdots \oplus p^{a_r} \oplus {\bf 0}_{m-r}
  $$
  where ${\bf 0}_{m-r}$ is a null square matrix of size $m-r$.
  The matrix $S$ is called the \emph{Smith Normal Form (SNF)} of $M$, and the elements $p^{a_i}$ the
  \emph{invariant factors}.
\end{definition}

\begin{remark}
  The valuation of the first coefficient\footnote{invariant factor?} of the SNF of a matrix
  $M \in \allmat_{n,n} \left( \QQ_p \right) $ is the minimum of the valuations of the matrix
  $M$'s terms (\simone{proof or reference}). In particular, the the SNF of matrix of $\mathcal{M}_n \left( \OK \right) $ have coefficients in $\ZZ_p$ .
 The $r = \text{rank} M$ first diagonals coefficients of $S$ are exactly its non-zero coefficient.
\end{remark}

@@

\section{Other questions}
\begin{itemize}
\item The projection of a real polyhedron is a real polyhedron (thanks to Fourier-Motzkin elimination procedure). Is it the same for $K$-polyhedra?
\item Annuli are semidefinite representable, we should remark/prove that they are not spectrahedra.
\end{itemize}
